Pesticides in small agricultural streams in Germany

### 2016-08-22 article.tex
abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% 150-200 words

Fehlt noch...
\end{abstract}

@@

%%% Word count
%% Figures  = 2400
% 3 big = 3*600 = 1800
% 2 small = 2*300 = 600

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \newcommand*\mycommand[1]{\texttt{\emph{#1}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% 150-200 words
Small streams are important refuge areas for biodiversity.
Although, small agricultural streams may be a high risk of pesticide pollution, relatively little is know on their chemical status.
Monitoring of chemical status is performed in Germany be the federal states for surveillance of chemical status and might shed some light also on small streams.

We compiled available monitoring data from federal states with a focus on small streams, resulting in a dataset of 2,918,604 measurements from 42,236 samples from 3,049 sampling sites in the years 2005-2014.
The dataset covered 484 different compounds that can be classified as pesticides.
We found a lack of data for small streams \textless 10 km\textsuperscript{2} catchment size.
Especially neonicotinoid insecticides and Chlorpyrifos showed exceedancas of regulatory acceptable concentrations (RACs), which could be related to agricultural land use.
However, a nation-wide assessment was hampered by a high heterogeneity between states.

Our result suggest that pesticides might be a major thread for aquatic life.
However, future monitoring programs need to be unified between states to provide more reliable assessments.

\todo{not finished yet}

%% Word
\end{abstract}

@@

@@

%%% Word count
% abstract    :
% 3 big(600)  : 1800
% 2 small(300): 600
% text body   : 3000 
% ackno       : 24
% ======================================
% total       :
